---
title: "Final Project - Group 05"
author: "Nikhil Bhosale, Pooja Bendale, Ssanidhya Barraptay"
date: "2022-11-19"
output:
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Github URL - https://github.com/Nikhil12121/514-Project-Group-5


## Section 1 - Visualizing the data

Importing the standard libraries and packages:

```{r include=FALSE}
library(tidyverse)
library(ggplot2)
library(rpart)
library('class')
library(corrplot)
library(RColorBrewer)
library(MLmetrics)
library(MASS)
require(webr)
```

#### We have imported the data from Cellphone.csv file and stored in the Cellphone variable. 

```{r}
Cellphone <- read.csv("C:\\Users\\ACER\\Desktop\\DATA ANALYTICS\\Cellphone.csv",header=TRUE, stringsAsFactors=FALSE)
```

#### 1.1 Displayig the summary of Cellphone data

```{r}
summary(Cellphone)
```
#### 1.2 To find out the Data type of all enteties: 

```{r}
str(Cellphone)
```
We have used str() to find out the datatype for each attribute.

#### 1.3 To determine the number of null values in given data.

```{r}
null_values <- sum(is.na(Cellphone)) 
null_values
```
From the above output we can see that their are 0 null values.

#### 1.4 To determine the numbers of duplicate values in given data.

```{r}
duplicate_values_old <- sum(duplicated(Cellphone))
duplicate_values_old
```
From the above output we can see that their are 0 duplicate values.

#### 1.5 To detrmine the correlations between all entities:

```{r}
mydata.cor = cor(Cellphone, method = "spearman")
corrplot(mydata.cor, method = "color", addCoef.col="grey", order = "AOE" ,number.cex=0.70 )
```

As seen above, we have represented the correlation matrix using the corrplot function.

## Section 2 - Graphical Overview

#### 2.1 Histogram to show number of Phones by Price
>we can plot graph using hist() function.

```{r}
price_Cellphone <- Cellphone$Price
hist(price_Cellphone)
```

>1. Maximum phones around 30 to 40 are having price range 1500 to 3000
>2. Approximately 10 phones are having price range from 3500 to 5000.
>3. Approximately 11 to 17 phones are having price ranges from minimum to 1500.

#### 2.1.1 To get detailed information regarding mean, Q1 and Q3 in Histogram :

```{r}
ggplot(Cellphone, aes(Price)) +
  geom_histogram(color = "darkblue", fill = "lightblue", bins = 20) +
  geom_vline(aes(xintercept = mean(Price)), color = "#000000", linewidth = 1.25) +
  geom_vline(aes(xintercept = mean(Price) + sd(Price)), color = "#000000", linewidth = 1, linetype = "dashed") +
  geom_vline(aes(xintercept = mean(Price) - sd(Price)), color = "#000000", linewidth = 1, linetype = "dashed") +
  scale_fill_gradient("Legend",low = "green", high = "blue")
```


Here, we have printed mean line and Q1 and Q3 lines in the Histogram.
And we could see that maximum data is lies around the mean line.

#### 2.2 Boxplot to show number Price of cell phones.

```{r}
price_Cellphone <- Cellphone$Price
boxplot(price_Cellphone)
summary(price_Cellphone)
```
Minimum value for price is approximately 500 and Max value is above 4000.
Having median is around 2200.
Price entity contains only one Outlier.

#### 2.3 Overlay Diagram - To plot the diagram for the price. 

>Overlay Histogram alog with Boxplot

```{r}
new_cellphone <- dplyr::mutate(Cellphone ,highlowprice = case_when(Price <= 1500 ~ 'low' ,Price > 1500 & Price <= 3000 ~ 'Medium' ,Price > 3000 ~ 'High'))
```

```{r}
par(mfrow=c(1,2))
ggplot(new_cellphone,aes(x = battery , fill = highlowprice)) + geom_histogram(alpha = 0.9, bins = 15,color = "black")
```
> 1. Battery ranges from 1500maH to 3000 are situated in medium price range. Low battery phone have price range between 0 to around 1700 
> 2. 0 to 2000 Battery range has only low battery phones ,and range - 2000 to 3000 we have mostly medium value phones along with a few low and high priced phones.
> 3. Phone having battery range from 3000 - 5000 are high priced phones. Medium and high  ranged phones lie between 3000 to 4500  maH battery.
> 4. Some outliers can be seen in medium and high priced devices as seen in the boxplot above.

```{r}
ggplot(data = new_cellphone ,mapping = aes(x = battery)) + geom_boxplot(aes( fill = highlowprice))
```


## Section 3 - Hypothesis Testing

#### 3.1 CASE 1 

**Parameters:**

Price and weight are the numerical measurements and the parameters of interest are population variance of price and weight.


**Hypotheses:**

*Null Hypothesis:* Population mean of Price is directly proportional to that of weight.

*Alternate Hypothesis:* Population mean of Price is not proportional to that of weight.

\[H_0: \mu_{P} = \mu_{W} \qquad H_1: \mu_{P} \ne \mu_{W}  \]

```{r}
t.test(Cellphone$Price, Cellphone$weight, var.equal = TRUE, conf.level = 0.95)
```

As we can see the p-value is less than α, we should reject the Null Hypothesis.
Similarly, We can define the test of proportionality of variances as follows:

  
 \[H_0: \sigma_P^2/\sigma_W^2 =1 \qquad H_1: \sigma_P^2/\sigma_W^2 \ne 1 \]

```{r}
var.test(Cellphone$Price, Cellphone$weight, alternative = "two.sided")
```
Here the p value is again less than α, hence we reject Null hypothesis.
As the statistic provides evidence against and in favor of alternate hypothesis

Below we have graphically represented the t-statistic.

```{r}
plot(t.test(Cellphone$Price, Cellphone$weight, var.equal = FALSE, conf.level = 0.95, alternative = "greater"))
```


#### 3.2 CASE 2 
**Parameters:**

The numerical measurements are ram and price, and the parameters of interest are population mean of ram and price.

**Hypotheses:**

*Null Hypothesis:* Population mean of ram is directly proportional to that of price.

*Alternate Hypothesis:* Population mean of ram is not proportional to that of price.

\[H_0: \mu_R =\mu_P \qquad H_1: \mu_R \ne \mu_P \]
```{r}
t.test(Cellphone$ram, Cellphone$Price, var.equal = TRUE, conf.level = 0.95)
```

As we can see the p-value is less than α, we should reject the Null Hypothesis.
Similarly, We can define the test of proportionality of variances as follows:

\[H_0: \sigma_R^2 /\sigma_P^2 = 1 \qquad H_1: \sigma_R^2 /\sigma_P^2 \ne 1 \]
```{r}
var.test(Cellphone$ram, Cellphone$Price, alternative = "two.sided")
```

Here the p value is again less than α, hence we reject Null hypothesis.
As the statistic provides evidence against and in favor of alternate hypothesis

Below we have graphically represented the t-statistic.

```{r}
plot(t.test(Cellphone$ram, Cellphone$Price, var.equal = FALSE, conf.level = 0.95))

```

## Section 4 - Linear Regression Using Akieke Information Theory
#### Using Scale to standardize the data
```{r}
cellData <- scale(Cellphone)
cellData <- as.data.frame(cellData)
```

## Using set seed to make sure we produce output every time we run the code 
```{r}
set.seed(30021)
```


#### 4.1 Train - Test Split

```{r}
#Splitting the dataset into 75% training and 25% testing
i = sample(2, nrow(cellData), replace = TRUE, prob = c(0.75,0.25))
CellPhone_Training <- cellData[i == 1,]
CellPhone_Testing <- cellData[i == 2,]
```

#### Dataset dimensions
```{r}
dim(CellPhone_Training) 
dim(CellPhone_Testing)
```

#### 4.2 Model 1 using AIC : Forward Model Propogation

```{r}
init_model <- lm(Price ~ 1, data = CellPhone_Training[,1:14])
all_model <- lm(Price ~ ., data = CellPhone_Training[,1:14])
forwardModel <- stepAIC(init_model, direction = "forward" , scope = formula(all_model))
```
#### 4.3 Summary of Forward Propogation Model
```{r}
summary(forwardModel)
```
#### 4.4 Analysis of Variance of Forward model
```{r}
forwardModel$anova
```
#### 4.5 Finding the Mean Absolute Error on the Testing Dataset for Forward Propogation Model
```{r}
forward_pred <-predict(object = forwardModel, newdata = CellPhone_Testing[,1:14])
MAE(y_pred = forward_pred, y_true = CellPhone_Testing$Price)
```
#### 4.6 Finding the Root Mean Squared Error on the Testing Dataset for Forward Propogation Model
```{r}
RMSE(y_pred = forward_pred, y_true = CellPhone_Testing$Price)
```
#### 4.7 Plot of result
```{r}
par(mfrow=c(2,2))
plot(forwardModel)
```


### Model 2: Backward Model Propogation

#### 4.8 To construct and define the backward model

```{r}
backward_model = stepAIC(all_model ,direction = "backward")
summary(backward_model)
backward_model$anova
```

#### 4.9 To calculate MAE and MSE for backward model

```{r}
backward_pred <-predict(object = backward_model, newdata = CellPhone_Testing[,1:14])
MAE(y_pred = backward_pred, y_true = CellPhone_Testing$Price)
RMSE(y_pred = backward_pred ,y_true = CellPhone_Testing$Price)
```

#### 4.10 Plotting the backward model 

```{r}
par(mfrow = c(2,2))
plot(backward_model)
```

